Artin Group Presentations Arising from Cluster Algebras

### 2014-07-24 Paper.tex
added some of emily's comments to aarons section

\begin{defn}

The associated Artin group $A_\Gamma$ is generated by $s_i,$ where there is one $s_i$ for each vertex $i$ in $\Gamma.$ These generators are subject to the following relations
\begin{itemize}
	\item[(R2)] With $m_{ij}$ as defined in ~\ref{mij_defn}, for all $i \neq j,$ we add the relations
	$\langle s_i,s_j \rangle^{m_{ij}}= \langle s_j,s_i \rangle^{m_{ij}}.$

@@

\begin{prop}
\label{cycle_types}
Let $\Gamma$ be a diagram of finite type. Then, a chordless cycle in the unoriented graph of $\Gamma$ is cyclically oriented in $\Gamma$. Furthermore, the unoriented graph underlying the cycle must either be a cycle such that all edges have weight 1, a triangle with two edges of weight 2 and one of weight 1, or a square with two opposite edges of weight 2 and two opposite edges of weight 1, as pictured below.

@@

\end{prop}
\begin{proof}
See \cite[Proposition 2.1]{BM13}.
\end{proof}

\begin{cor}
\label{local_three_picture}
Let $\Gamma$ be a graph of finite type and suppose there are three vertices, labeled $i,j,k$ with both $i,j$ connected to $k.$ Then mutation at $k$ on the induced subdiagram appear as in one of the following figures, either from left to right or right to left, up to switching $i$ and $j,$

@@

\end{cor}
\begin{proof}
See \cite[Corollary 2.3]{BM13}.
\end{proof}

@@

In order to prove our main result, Theorem ~\ref{thm:main}, we must first define the Artin Group associated to a finite type diagram. This definition will be similar to that made in \cite{BM13} at the beginning of Section 3, except that we shall not require $s_i^2 = e.$ Since Artin Groups are very similar to coxeter groups, with the caveat that the generators are not involutions, we will be able to use these modified relations to great effect.

@@

\end{note}
\begin{defn}
For $M \in M_{n \times n}(\mathbb Z \cup \infty)$ a matrix which whose entries can take values in the real numbers or infinity, satisfying $m_{i,j} = m_{j,i}$ we define the associated {\it Artin Group} in terms of generators and relations by
\begin{align*}
	A = \langle x_1,\ldots, x_n| \langle x_i,x_j \rangle^{M_{i,j}}\forall i,j \text{ with } m_{i,j}<\infty \rangle,
\end{align*}
\end{defn}

\begin{rem}
Each Artin group has an associated Coxeter Group defined by adding in the additional relations $s_i^2 = 1$ for all $i.$ An Artin group is said to be of {\it finite type} if its associated Coxeter group is of finite type. To each Artin group of finite type we can assign it the same Dynkin diagram which is assigned to the Coxeter group associated to the Artin group.
\end{rem}

@@

Recall from Section \ref{sec:main_definitions} that for $\Gamma$ a diagram of finite type, we define the associated Artin Group as follows. The associated Artin group $A_\Gamma$ is generated by $s_i,$ where there is one $s_i$ for each vertex $i$ in $\Gamma.$ These generators are subject to the following relations
\begin{itemize}
	\item[(R2)] With $m_{ij}$ as defined in ~\ref{mij_defn}, for all $i \neq j,$ we add the relations
	$\langle s_i,s_j \rangle^{m_{ij}}= \langle s_j,s_i \rangle^{m_{ij}}.$

\begin{rem}
In the above definition, the chordless cycle is ordered, which means that two cycles are considered different if they are cyclic rotations of each other.
\end{rem}

\begin{rem}
We purposely include relations $(R2),(R3)$ but not $(R1)$ in order to make our relation labeling analogous to that of \cite{BM13} at the beginning of Section 3. Note that if we add the additional relation $(R1)$ as defined at the beginning of Section 3 of \cite{BM13} (namely, if we add $s_i^2 = e$ for all vertices $i$ in $\Gamma$), then we will precisely obtain the group $W_\Gamma$ as defined at the beginning of section 3 in \cite{BM13}.
\end{rem}

@@

\begin{rem}
Note that if $\Gamma$ is the graph associated to a Dynkin diagram, then $W_\Gamma$ as we have defined it is precisely the corresponding Artin group corresponding to that Dynkin diagram. This occurs because, in this case, we have no cycles in $\Gamma,$ and so we only have relation of the form $(R2'),$ which define the Artin Group.
\end{rem}

@@

>>>>

\begin{defn}
The associated Artin group $A_\Gamma$ is generated by $s_i,$ where there is one $s_i$ for each vertex $i$ in $\Gamma.$ These generators are subject to the following relations
\begin{itemize}
	\item[(R2)] With $m_{ij}$ as defined in ~\ref{mij_defn}, for all $i \neq j,$ we add the relations
	$\langle s_i,s_j \rangle^{m_{ij}}= \langle s_j,s_i \rangle^{m_{ij}}.$

@@

\begin{prop}
\label{cycle_types}
\cite[Proposition 2.1]{BM13} Let $\Gamma$ be a diagram of finite type. Then, a chordless cycle in the unoriented graph of $\Gamma$ is cyclically oriented in $\Gamma$. Furthermore, the unoriented graph underlying the cycle must either be a cycle such that all edges have weight 1, a square with two opposite edges of weight 2 and two opposite edges of weight 1, as pictured below, or a triangle with two edges of weight 2 and one of weight 1.

@@

\end{prop}

\begin{cor}
\label{local_three_picture}
\cite[Corollary 2.3]{BM13} Let $\Gamma$ be a graph of finite type and suppose there are three vertices, labeled $i,j,k$ with both $i,j$ connected to $k.$ Then mutation at $k$ on the induced subdiagram appear as in one of the following figures, either from left to right or right to left, up to switching $i$ and $j,$

@@

\end{cor}

@@

In order to prove our main result, Theorem ~\ref{thm:main}, we must first define the Artin group associated to a finite type diagram. This definition will be similar to that made in \cite{BM13} at the beginning of Section 3, except that we shall not require $s_i^2 = e.$ Since Artin Groups are very similar to coxeter groups, with the caveat that the generators are not involutions, we will be able to use these modified relations to great effect.

@@

\end{note}
\begin{defn}
\cite[Beginning of section 1.2]{artin} \todo{put reference for artin, found at the bottom, in bibliography, but I don't know how to use this bibliography format.}
For $M \in M_{n \times n}(\mathbb Z \cup \infty)$ a matrix whose entries can take values in the real numbers or infinity, satisfying $M_{i,j} = M_{j,i}$ we define the associated {\it Artin group} in terms of generators and relations by
\begin{align*}
	A = \langle x_1,\ldots, x_n| \langle x_i,x_j \rangle^{M_{i,j}}\forall i,j \text{ with } m_{i,j}<\infty \rangle,
\end{align*}
\end{defn}

\begin{rem}
Each Artin group has an associated Coxeter group defined by adding in the additional relations $s_i^2 = 1$ for all $i.$ An Artin group is said to be of {\it finite type} if its associated Coxeter group is of finite type. To each Artin group of finite type we can assign it the same Dynkin diagram which is assigned to the Coxeter group associated to the Artin group.
\end{rem}

@@

Recall from Section \ref{sec:main_definitions} that for $\Gamma$ a diagram of finite type, we define the associated Artin group as follows. The associated Artin group $A_\Gamma$ is generated by $s_i,$ where there is one $s_i$ for each vertex $i$ in $\Gamma.$ These generators are subject to the following relations
\begin{itemize}
	\item[(R2)] With $m_{ij}$ as defined in ~\ref{mij_defn}, for all $i \neq j,$ we add the relations
	$\langle s_i,s_j \rangle^{m_{ij}}= \langle s_j,s_i \rangle^{m_{ij}}.$

\item[(R3)] Let $(i_0,i_1,\ldots,i_{d-1})$ be an ordered tuple such that the subgraph of $\Gamma$ on the vertices $(i_0,\ldots, i_{d-1})$ is a chordless cycle, with edges of nonzero weight from $i_k$ to $i_{k+1},$ where subscripts $k$ are taken $\pmod d.$ If $(i_0,\ldots, i_{d-1})$ is such an ordered tuple, and additionally,
\begin{enumerate}
	\item All edges in the chordless cycle are of weight 1 or 2 and the edge $i_{d-1}\rightarrow i_0$ has weight 2.
	\item All edges in the chordless cycle have weight $1.$
\end{enumerate}
we include the relation
\begin{align*}
	s_{a}s_{a+1}^{-1}s_{a+2}^{-1}\dots s_{a-2}^{-1}s_{a-1}s_{a-2}s_{a-3}\dots s_{a+1} = s_{a+1}^{-1}\dots s_{a-3}^{-1}s_{a-2}^{-1}s_{a-1}s_{a-2}\dots s_{a+1}s_{a},
\end{align*}
where subscripts are taken $\pmod d.$ We will denote this relation by r(a, a+1). 
\end{itemize}
\end{defn}

\begin{rem}
In the above definition, the tuple cycle is ordered, and so we may have multiple relations corresponding to the same set $\{i_0,\ldots, i_{d-1}\},$ corresponding to cyclic rotations of the tuple $(i_0,\ldots, i_{d-1}).$ However, we shall see in Section ~\ref{sec:one_relation} that many of these relations are redundant.
\end{rem}

\begin{rem}
We purposely include relations $(R2),(R3)$ but not $(R1)$ in order to make our relation labeling analogous to that of \cite{BM13} at the beginning of Section 3. Note that if we add the additional relation $(R1)$ as defined at the beginning of Section 3 of \cite{BM13} (namely, if we add $s_i^2 = e$ for all vertices $i$ in $\Gamma$), then we will precisely obtain the group $W_\Gamma$ as defined at the beginning of rem 3 in \cite{BM13}.
\end{rem}

@@

\begin{rem}
Note that if $\Gamma$ is the graph associated to a Dynkin diagram, then $W_\Gamma$ as we have defined it is precisely the corresponding Artin group corresponding to that Dynkin diagram. This occurs because, in this case, we have no cycles in $\Gamma,$ and so we only have relation of the form $(R2'),$ which define the Artin group.
\end{rem}

@@

artin: http://people.brandeis.edu/~charney/papers/RAAGfinal.pdf
